### 2010-08-05 docs/planar_invsq_base/basestate.tex
non-uniform is not tri-diagonal

Consider the above non-uniform grid spacing,
where $\dr_c = 2 \dr_f$.  Here, the discretization of the Laplacian-like term is more complex.
We want to compute
\begin{equation}
\frac{\partial}{\partial r} \left [ \gammabar p_0 \frac{\partial \dw}{\partial r} \right ]_{j-\half}
\end{equation}
This is to be centered at $j-\half$, which we accomplish by averaging the two fine grids and then
differencing:
\begin{equation}
\frac{\partial}{\partial r} \left [ \gammabar p_0 \frac{\partial \dw}{\partial r} \right ]_{j-\half} =
\frac{1}{\dr_c} \left \{ \frac{1}{2} \left [
      \left ( \gammabar p_0 \frac{\partial \dw}{\partial r} \right )_{j+1} +
      \left ( \gammabar p_0 \frac{\partial \dw}{\partial r} \right )_{j} \right ]
   - \left ( \gammabar p_0 \frac{\partial \dw}{\partial r} \right )_{j-1} 
\right \}
\end{equation}

>>>>

Consider the above non-uniform grid spacing,
where $\dr_c = 2 \dr_f$.  Here, the discretization of the Laplacian-like term is more complex.
We want to compute
\begin{equation}
\frac{\partial}{\partial r} \left [ \gammabar p_0 \frac{\partial \dw}{\partial r} \right ]_{j-\half}
\end{equation}
This is to be centered at $j-\half$, which we accomplish by averaging the two fine grids and then
differencing:
\begin{equation}
\frac{\partial}{\partial r} \left [ \gammabar p_0 \frac{\partial \dw}{\partial r} \right ]_{j-\half} =
\frac{1}{\dr_c} \left \{ \frac{1}{2} \left [
      \left ( \gammabar p_0 \frac{\partial \dw}{\partial r} \right )_{j+1} +
      \left ( \gammabar p_0 \frac{\partial \dw}{\partial r} \right )_{j} \right ]
   - \left ( \gammabar p_0 \frac{\partial \dw}{\partial r} \right )_{j-1} 
\right \}
\end{equation}
Expanding the $\partial \dw / \partial r$ terms results in a equation depending on $\dw$ at
4 different edge locations---this no longer fits into the tri-diagonal format used in the
uniform grid case.  In detail, it becomes:
\begin{eqnarray}
\frac{\partial}{\partial r} \left [ \gammabar p_0 \frac{\partial \dw}{\partial r} \right ]_{j-\half} &=& 
\frac{1}{\dr_c} \left \{  \frac{1}{2} \left [
      \left ( \gammabar p_0 \right )_{j+1} \frac{(\dw)_{j+\thalf} - (\dw)_{j+\half}}{\dr_f} +
      \left ( \gammabar p_0 \right )_{j}   \frac{(\dw)_{j+\half} - (\dw)_{j-\half}}{\dr_f}  \right ] \right .  \nonumber \\
&& \qquad \left .  - \left ( \gammabar p_0 \right )_{j-1} \frac{(\dw)_{j-\half} - (\dw)_{j-\thalf}}{\dr_c}  
\right \}
\end{eqnarray}
which has terms proportional to $(\dw)_{j-\thalf}$, $(\dw)_{j-\half}$, $(\dw)_{j+\half}$, and $(\dw)_{j+\thalf}$
